Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-04-20 paper/paper.tex
Word
Unword

A graph $G$ is \emph{isomorphic} to another graph $H$ if there exists a bijective function $f :
\operatorname{V}(G) \rightarrow \operatorname{V}(H)$ which preserves edges and non-edges, i.e.\
$\forall (u, v) \in \operatorname{V}(G) \times \operatorname{V}(G), (u, v) \in \operatorname{E}(G)
\Leftrightarrow (f(u),f(v)) \in \operatorname{E}(H)$.  A \emph{common subgraph} of two graphs $G$
and $H$ is a graph isomorphic to subgraphs of $G$ and $H$. A \emph{common connected subgraph} is a
common subgraph which is connected.  A \emph{Maximum Common Subgraph}, or MCS (resp. \emph{Maximum
Common Connected Subgraph}, or MCCS) is a common subgraph (resp.\ common connected subgraph) which has
a maximum number of vertices.

@@

Then, in \cref{mccs}, we consider the MCCS problem. For the CP approach, we may add a global
connectedness constraint to the model. Alternatively, we may use a special branching rule
\cite{DBLP:conf/mco/VismaraV08} to grow connected subgraphs only. These two techniques may
be combined, and we experimentally show that the best results are obtained when combining them.
When solving the MCCS problem with a clique-based approach, neither technique seems directly viable
with an association graph encoding.  However, we show that it is possible to adapt the combined
branching and bounding rule used by modern clique algorithms to maintain connectedness during
search.  We compare the clique-based approach with the best CP variant for the MCCS, and we show
that it outperforms CP on labelled graphs, whereas it is outperformed by CP on unlabelled graphs.

>>>>

A graph $G$ is \emph{isomorphic} to another graph $H$ if there exists a bijective function $f :
\operatorname{V}(G) \rightarrow \operatorname{V}(H)$ which preserves edges and non-edges, i.e.\
$\forall (u, v) \in \operatorname{V}(G) \times \operatorname{V}(G), (u, v) \in \operatorname{E}(G)
\Leftrightarrow (f(u),f(v)) \in \operatorname{E}(H)$.  A \emph{common subgraph} of two graphs $G$
and $H$ is a graph isomorphic to subgraphs of both $G$ and $H$. A \emph{common connected subgraph} is a
common subgraph which is connected.  A \emph{Maximum Common Subgraph}, or MCS (resp. \emph{Maximum
Common Connected Subgraph}, or MCCS) is a common subgraph (resp.\ common connected subgraph) which has
a maximum number of vertices.

@@

Then, in \cref{mccs}, we consider the MCCS problem. For the CP approach, we may add a global
connectedness constraint to the model. Alternatively, we may use a special branching rule
\cite{DBLP:conf/mco/VismaraV08} to grow connected subgraphs only. These two techniques may
be combined, and we experimentally show that the best results are obtained when combining them.
When solving the MCCS problem with a clique-based approach, neither technique seems directly viable
with an association graph encoding.  However, we show that it is possible to adapt the combined
branching and bounding rule used by modern clique algorithms to maintain connectedness during
search.  We compare the clique-based approach with the best CP variant for MCCS, and we show
that it outperforms CP on labelled graphs, whereas it is outperformed by CP on unlabelled graphs.
